EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-17 draft.tex
Deleting addressed comments and adding some results

From these parameters, we give more importance in this paper to the number of
populations, because they are the basic unit of work that can be executed in
parallel. Together with the size of each population and the number of
generations, this parameter determines the maximum number of function
evaluations for a single iteration. We do not have control over each algorithm's
complexity, but future analyses could focus on balancing populations according
to this.

@@

% I think this is now a bit redundant or we need to move it to the parent section - M
% But is a good intro to the results.

@@

% Introduction saying why we are measuring this, how it's related to the objectives of the paper - JJ
% This is done on the parent section, I renamed the sections to clarify this - M
To measure the speedup obtained by the addition of workers, we will use the
number of evaluations per second, instead of the time required to finish an
instance of a problem. The reason for this is that in some cases reaching the
desired target can require less work. We are going to measure the total increase
of work done in a second by adding more workers. The baseline for the comparison
will be the algorithm with a single worker, and the minimum amount of work available will be five
populations. This number is selected because the controller needs at least
three populations to migrate individuals between them, and we add two more to
keep even a single worker busy. Figure \ref{fig:spworker:evalspersecond} 
shows the number of function evaluation per second, achieved by a certain number of
workers, for every problem dimension, for five and ten dimensions of $f_4$.  % Why did you choose f4? - JJ This is mentioned on the setup - M

@@

Table~\ref{tab:speedup:test} shows the speedup obtained taking as the baseline
the previous configuration, for example, when increasing from four to eight
workers, and the p-rate for the left-tailed Wilcoxon test. There was an
increment in all cases, but again, for smaller dimensions, five populations with
fewer workers is a better option (see values underlined in the table) with the best speedup, achieved for 40 dimensions, shown in bold. The worst speed was going from four to eight workers 
at higher dimensions (underlined in the table). 
For ten populations, adding more workers resulted in a linear speedup, % don't understand this - JJ % Me either - M, rewritten  
but the best speedup is obtained when increasing from four to eight workers at 40 dimensions
(shown in bold).

% No idea where this fits in. I think it's the second question in 7, 
% so it should probably be a subsection - JJ
% done - M

@@

In order to run this experiment, we just needed to edit a configuration file and run 
the experiments. The plots presented in the results are generated by the BBOB framework
from the JOSN log file of each run. There was no additional setup needed.

>>>>

From this description it can be deduced that we give more importance in this paper to the number of
populations, since they are the basic unit of work that can be executed in
parallel. Together with the size of each population and the number of
generations, this parameter determines the maximum number of function
evaluations for a single iteration. We do not have control over each algorithm's
complexity, but future analyses could focus on balancing populations and number of worker nodes according
to this.

@@

% I think this is now a bit redundant or we need to move it to the parent section - M
% But is a good intro to the results.
% OK - JJ

@@

% Introduction saying why we are measuring this, how it's related to the objectives of the paper - JJ
% This is done on the parent section, I renamed the sections to clarify this - M
To measure the speedup obtained by the addition of workers, we will use the
number of evaluations per second, instead of the time required to finish an
instance of a problem. The reason for this is that in some cases reaching the
desired target can require less work. We are going to measure the total increase
of work done in a second by adding more workers. The baseline for the comparison
will be the algorithm with a single worker, and the minimum amount of work available will be five
populations. This number is selected because the controller needs at least
three populations to migrate individuals between them, and we add two more to
keep even a single worker busy. Figure \ref{fig:spworker:evalspersecond} 
shows the number of function evaluation per second, achieved by a certain number of
workers, for every problem dimension, for five and ten dimensions of $f_4$.

@@

Table~\ref{tab:speedup:test} shows the speedup obtained taking as the baseline
the previous configuration, for example, when increasing from four to eight
workers, and the p-rate for the left-tailed Wilcoxon test. There was an
increment in all cases, but again, for smaller dimensions, five populations with
fewer workers is a better option (see values underlined in the table) with the best speedup, achieved for 40 dimensions, shown in bold. The worst speed was going from four to eight workers 
at higher dimensions (underlined in the table). 
For ten populations, adding more workers resulted in a linear speedup, 
but the best speedup is obtained when increasing from four to eight workers at 40 dimensions
(shown in bold).

@@

In order to run this experiment, we just needed to edit a configuration file and start it up. The plots presented in the results are generated by the BBOB framework
from the JOSN log file for each run. There was no additional setup needed, proving how this framework is able to not only offer an reproducible way to run experiments, but also how easily it interfaces with other common tools in the EC ecosystem.
